\documentclass[a4paper,11pt]{moderncv}

% moderncv themes
\moderncvtheme[blue]{classic}

% Character encoding
\usepackage[utf8]{inputenc}

% Personal data
\firstname{Joris}
\lastname{de Josselin de Jong}
\title{Kubernetes Engineer}
\address{Maarssen, Netherlands}

\begin{document}

\makecvtitle

\section{Professional Experience}

\cventry{Jan 2022 -- Present}{Kubernetes Engineer}{True B.V. / TrueFullstaq}{Amsterdam, Netherlands}{}{
\begin{itemize}
    \item \textbf{Team Involvement:}
    \begin{itemize}
        \item Member of the 'Speedboat' team, focusing on redesigning the company's infrastructure approach.
    \end{itemize}
    \item \textbf{Migration Projects:}
    \begin{itemize}
        \item Migrated and updated critical applications (Keycloak, Rocket-chat, Trident, Cert-manager, CloudNativePostgresOperator) within Kubernetes environments.
    \end{itemize}
    \item \textbf{Configuration Management:}
    \begin{itemize}
        \item Created SaltStack formulas and developed a testing framework using Kitchen and Pre-commit.
        \item Utilized Renovate for lifecycle management.
    \end{itemize}
    \item \textbf{Monitoring and Automation:}
    \begin{itemize}
        \item Integrated Grafana and Prometheus with SaltStack master, creating custom dashboards.
        \item Implemented automation solutions using Terraform, Python, Bash, Ansible, and Go to streamline operations.
    \end{itemize}
    \item \textbf{Client Engagement:}
    \begin{itemize}
        \item Led client onboarding initiatives through technical workshops, presentations, and hands-on training.
        \item Created and led a workshop about Kubernetes operators, see this repo for more: \url{https://github.com/jorisdejosselintrue/operator-workshop-edgecase-2024}.
        \item Handled support tickets ranging from low-level debugging to complex issues.
    \end{itemize}
    \item \textbf{Container Orchestration:}
    \begin{itemize}
        \item Focused on container orchestration and cloud-native solutions.
        \item Maintained Kubernetes infrastructure running on RKE1 (Rancher Kubernetes Engine) and Azure Kubernetes Service (AKS).
    \end{itemize}
    \item \textbf{ISO:}
    \begin{itemize}
        \item Assisted in obtaining the \href{https://partner.microsoft.com/en-my/partnership/specialization/kubernetes}{Kubernetes on Microsoft Azure}  specialization for TrueFullstaq.
    \end{itemize}
\end{itemize}}

\cventry{Jan 2021 -- Jan 2022}{Linux Engineer}{True B.V.}{Amsterdam, Netherlands}{}{
\begin{itemize}
    \item \textbf{Infrastructure Support:}
    \begin{itemize}
        \item Supported Linux-based infrastructure.
        \item Implemented system administration best practices.
        \item Developed and updated Ansible playbooks.
    \end{itemize}
\end{itemize}}

\cventry{Sep 2020 -- Jan 2021}{System Design Engineer}{Alstom}{Utrecht, Netherlands}{}{
\begin{itemize}
    \item \textbf{System Design:}
    \begin{itemize}
        \item Contributed to system design and engineering projects based on VMware ESXi.
        \item Developed technical solutions for transportation infrastructure.
    \end{itemize}
\end{itemize}}

\cventry{Feb 2020 -- Aug 2020}{Intern}{Alstom}{Utrecht, Netherlands}{}{
\begin{itemize}
    \item \textbf{Internship Experience:}
    \begin{itemize}
        \item Gained practical experience in engineering processes.
        \item Created a thesis on how current applications could run on Kubernetes.
    \end{itemize}
\end{itemize}}

\section{Education}
\cventry{2015 -- 2020}{Bachelor of System and Network Engineering}{Hogeschool Utrecht}{Utrecht, Netherlands}{}{
\begin{itemize}
    \item Completed Bachelor's degree in System and Network Engineering.
\end{itemize}}

\section{Technical Skills}
\cvitem{Platforms}{Kubernetes, Linux, OpenNebula, VyOS, Azure}
\cvitem{Configuration Management}{Ansible, Saltstack, Terraform}
\cvitem{Monitoring}{Grafana (Cloud), Prometheus}
\cvitem{Programming Languages}{Python, Bash, Go, HCL}
\cvitem{Applications}{Keycloak, Rocket-chat, NetApp, Cert-manager, Helm, Gitlab-CI, Vault, CloudNativePostgresOperator (CNPG), Pre-commit, Renovate, Harbor}

\section{Hobbies}
\cvitem{Magic The Gathering}{Playing and collecting Magic The Gathering cards and participating in drafts with friends.}
\cvitem{Hosting my own stuff}{Recently set up Calibre on Kubernetes to sync all my books automatically with my Kobo E-reader.}
\cvitem{Bouldering}{Enjoying indoor rock climbing and bouldering activities.}
\cvitem{Gaming}{Playing various video games during my free time.}

\section{Additional Information}
\cvitem{CV Availability}{This CV is available on \href{https://github.com/jorisdejosselin/joris-cv-latex}{GitHub} and the PDF can be downloaded from the releases section.}

\end{document}